---
title: "Exploratory Analysis of Chickweight Data"
author: "Daniel N Quansah"
date: "`r Sys.Date()`"
output: 
  html_document: 
    theme: journal
    highlight: espresso
    toc: yes
---

### load library

```{r}
library("tidyverse")
```

### load data and view dimensions
```{r chickweight}
data <- ChickWeight
dim(data)

head(data)
```
### compute the descriptives of the chickweight data
```{r}
summary(data)
```


### Aggregate the mean weight depending on the diet fed to chicks
```{r}
dw <- aggregate(weight~Diet, data, mean)
dw
```

### plot the mean weight per diet
```{r}
ggplot(dw, aes(x=Diet, y=weight)) + geom_col(width = 0.75, fill="brown2")+
  geom_text(label=round(dw$weight,2), size=4,vjust=-0.3)+
  theme_minimal() + ggtitle("Mean chickweight Per Diet")
```

***which diet produced chicks with the highest weight?***

### Compute the maximum weight per diet
```{r}
wd <- aggregate(weight~Diet, data, max)
wd
```

### Generate a graphical representation of chicks with highest weight
```{r}
ggplot(wd, aes(Diet, weight)) + geom_col(fill="green4", width =0.85 )+theme_light()+
  geom_text(label=wd$weight,size=4,vjust=-0.25)+
  ggtitle("Maximum weight of chick per diet")
```

***How does the weight of chicks respond to time?***

### Mean Chickweight computed over time 
```{r}
wt <- aggregate(weight~Time, data, mean)
wt
```
### Plot of mean chickweight over time
```{r}
ggplot(wt, aes(x=Time, y=weight)) + geom_line(stat = "identity",inherit.aes = TRUE)+
  theme_get()+geom_smooth(alpha=0.2, linewidth=1)+
  ggtitle("Mean Growth trend of chicks over time")
```

***How does the weight of each diet change over time?***

### Plot of Weight of each diet over the 21day time period
```{r}
aggregate(data$weight,by=list(time=data$Time,diet=data$Diet), FUN = mean)
dt <- aggregate(weight~Diet+Time, data, mean)
ggplot(dt, aes(x=Time, y=weight,colour=Diet)) + geom_line()+
  theme_bw()+
  geom_point(alpha=0.3)+
  geom_smooth(alpha=0.2, linewidth=1)+
  ggtitle("Weight over time per diet")
```

```{r}
sessionInfo()
```


***This is my first rmarkdown document***